\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, margin=0.75in,top=0.35in]{geometry}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{setspace}
% \usepackage{parskip}
\setlist{topsep=2mm, parsep=1.75mm, itemsep=0.2em}

\usepackage{tgschola}
\usepackage[T1]{fontenc}

\usepackage{changepage}

\hyphenpenalty=10000


\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\thispagestyle{empty}
\setlength{\parindent}{0pt}


\begin{document}

\setstretch{1.20}

    \newcommand{\header}[1]{ 
        \vspace{4mm}
        {\large \noindent \textbf{#1}}
        \vspace{2mm}
        \hrule
        \vspace{3mm}
    }

    \begin{center}
        
        {\LARGE \textbf{Wesley Weisenberger}}
    
        \vspace{2mm}

        {\large Berkeley, CA  $\mid$ (805) 270-6573 
            $\mid$
            % \href{mailto:wesley@berkeley.edu}{wesley@berkeley.edu}
            \href{mailto:wesleynw@pm.me}{wesleynw@pm.me}

        }

    \end{center}


    \header{WORK EXPERIENCE}

    \begin{adjustwidth}{1em}{1em}


    \textbf{Jamba Juice} \hfill Summer 2022
    \\\textit{Team Lead}
    \\San Luis Obispo, CA
    \begin{itemize}
        \item Took orders for customers and handled payments.
        \item Made 30+ kinds of drinks and smoothies for customers, accomodating custom orders.
        \item Drinks required familiarity with detail oriented recipes to produce consistent results.
        \item Lead and manage store acting as manager in charge of the store.
        \item Managed POS systems, cash registers, and counting safe and cash registers at end of day.
    \end{itemize}

    \vspace{7mm}

    \textbf{Vons/Safeway}\hfill Summer 2021
    \\ \textit{Courtesy Clerk} 
    \\San Luis Obispo, CA
    \begin{itemize}
        \item Bagged groceries for shoppers.
        \item Managed upkeep of general store area: floors, shopping carts.
        \item Helped shoppers find specific items throughout the store.
        \item Managed self-checkout stations and helped customers with problems they encountered.
    \end{itemize}


    \textbf{Asunction Valley Farms}\hfill Aug 2019 - Jan 2020
    \\ \textit{Farm hand} 
    \\Templeton, CA
    \begin{itemize}
        \item 10-hour days consisted of helping with various tasks around a ranch/farm.
        \item Fed and took care of 10+ horses.
        \item Maintained cleanliness around the farm and ensured farm equipment was working.
    \end{itemize}
        
    \end{adjustwidth}

    
    \header{EDUCATION}

        \begin{adjustwidth}{1em}{1em}

            \textbf{University of California, Berkeley} 
            \hfill 
            \textbf{Expected Graduation:} May 2024 \\\\
            Bachelor of Arts in Computer Science, Minor in Data Science \hfill  \textbf{GPA:} 3.7

            \vspace{2.5mm}

        \end{adjustwidth}

    
\end{document}
