\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, margin=0.4in,top=0.35in]{geometry}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
% \usepackage{parskip}
\setlist{topsep=1mm, parsep=1.75mm, itemsep=-0.1em}

\usepackage{tgschola}
\usepackage[T1]{fontenc}

\usepackage{changepage}

\hyphenpenalty=10000


\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\thispagestyle{empty}
\setlength{\parindent}{0pt}


\begin{document}

    \newcommand{\header}[1]{ 
        \vspace{4mm}
        {\large \noindent \textbf{#1}}
        \vspace{1.5mm}
        \hrule
        \vspace{2mm}
    }

    \begin{center}
        
        {\LARGE \textbf{Wesley Weisenberger}}
    
        \vspace{2mm}

        {\large Berkeley, CA  $\mid$ (805) 270-6573 
            $\mid$
            % \href{mailto:wesley@berkeley.edu}{wesley@berkeley.edu}
            \href{mailto:wesley@berkeley.edu}{wesley@berkeley.edu}

        }

    \end{center}

    
    \header{EDUCATION}

        \begin{adjustwidth}{1em}{1em}

            \textbf{University of California, Berkeley} 
            \hfill 
            \textbf{Expected Graduation:} May 2024 \\
            Bachelor of Arts in Computer Science, Minor in Data Science \hfill  \textbf{GPA:} 3.7

            \vspace{2.5mm}

            \textbf{Relevant Coursework:}
                Structure and Interpretation of Computer Programs, 
                Data Structures, \\
                Computer Architecture,
                Discrete Math and Probability Theory, 
                Designing Information Devices and Systems I \& II, \\
                Database Systems, 
                Computer Security,
                Foundations of Data Science,
                Principles and Techniques of Data Science, \\
                Human Contexts and Ethics of Data, 
                Advanced Linux System Administration,
                Calculus I \& II

        \end{adjustwidth}

            
    \header{WORK EXPERIENCE}

    \begin{adjustwidth}{1em}{1em}


        \textbf{Undergraduate Research Apprentice Program} \hfill August 2022 -- Present
        \\ \textit{Data Science Student Researcher}
        \begin{itemize}
            \item Researching under Professor Johnathan Marshall in the UC Berkeley Legal Studies Department.
            \item Using text data mining to understand patterns and changes in 18th-19th Century criminal law.
            \item Constructing RegEx classifiers to impute class on 16,000+ Old Bailey Online corpus criminal cases.
        \end{itemize}

        \vspace{1mm}

        \textbf{UC Berkeley Division of Computing, Data Science, and Society} \hfill August 2021 -- May 2022
        \\ \textit{Data 8 (Data Science Foundations) Academic Intern}
        \begin{itemize}
            \item Assisted 30+ students in weekly labs with debugging and reinforcing programming concepts.
            \item Prepared and presented enrichment material for students to guide development in mastering data science problems.
            \item Topics included regression, classification algorithms, probabilistic distributions, SQL, and sampling methods.
        \end{itemize}

        % \textbf{Open Computing Facility} \hfill Fall 2020 -- Present
        % \begin{itemize}
        %     \item Maintaining campus computing infrastructure such as web hosting, printing, and computer lab.
        %     \item Performing system administration of servers and desktops used by hundreds of students each day.
        %     \item Teach various classes on Linux techniques and skills.
        % \end{itemize}

        
    \end{adjustwidth}

    

    \header{PROJECTS}

    \begin{adjustwidth}{1em}{1em}

        \textbf{End to End Encrypted File Sharing System -- Go} \hfill Spring 2023
        \begin{itemize}
            \item Designed and developed an API that allows users to upload, append to, delete files.
            \item API also supports file sharing between users and revocation of file access.
            \item Custom suite of tests written to ensure that file integrity and confidentiality were maintained even after any malicious action on the server.
        \end{itemize}

        \vspace{1mm}

        \textbf{Discord Bot -- Python} \hfill Spring 2022
        \begin{itemize}
            \item Enabled users to query images from an aggregated search engine, then manipulate, rasterize, or edit said images through text commands and macros.
            \item Self-hosted Docker environment facilitated error-handling and networking between Python container, search engine, and Linux system used for processing images.
        \end{itemize}

        \textbf{Gitlet -- Java} \hfill Fall 2021 
        \begin{itemize}
            \item Custom version control system modeled with functionality modeled after Git.
            \item Supports file tracking, branching, merging, and remote repositories.
            \item Implemented custom data structures to enable constant-time file lookup, hashing to handle "diffs" and to prevent file collisions, and merge conflict handling.
        \end{itemize}

        \vspace{1mm}

        \noindent \textbf{Weather Station -- C, HTML, Javascript} \hfill Spring 2021
        \begin{itemize}
            \item Constructed a custom battery-powered Arduino weather monitoring circuit system which pushed data to a database on a locally hosted Linux web server, accessible to the internet. 
            \item Self-hosted website to display and visualize weather data and trends. Website also gave users the ability to pull more recent weather measurements from the device.
        \end{itemize}

        
    \end{adjustwidth}

    

    \header{TECHNICAL SKILLS}

    \begin{adjustwidth}{1em}{1em}
        
        \textbf{Languages}: Python, Java, C, Go, SQL, HTML, CSS, Javascript, PHP, Swift, RISC-V Assembly
    
        \vspace{1mm}

        \textbf{Tools:} Git, Linux, Docker, NumPy, Pandas, Matplotlib, Seaborn, Scikit-learn, \LaTeX, MongoDB, RegEx

    \end{adjustwidth}

    
\end{document}
