\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, margin=0.8in,top=0.5in]{geometry}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{topsep=1mm, parsep=1.75mm}
% \usepackage[none]{hyphenat}
% \hyphenpenalty=10000

\usepackage[T1]{fontenc}
\usepackage{tgschola}

\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}


\begin{document}

    \newcommand{\header}[1]{ 
        \vspace{5mm}
        {\large \noindent \textbf{#1}}
        \vspace{1.5mm}
        \hrule
        \vspace{3.5mm}
    }

    % \newcommand{\resumesection[]}

    \setlist[itemize]{itemsep=-0.4em}

    \thispagestyle{empty}

    \noindent {\huge \textbf{Wesley Weisenberger}}
    
    \vspace{1.5mm}

    \noindent {\Large Berkeley, CA  $\mid$ 805.270.6573 $\mid$ 
    \href{mailto:wesley@berkeley.edu}{wesley@berkeley.edu}
    $\mid$ 
    \href{https://github.com/wesleynw}{github.com/wesleynw}}
        
    \vspace{-2mm}

    \header{EDUCATION}

        \noindent \textbf{University of California, Berkeley} 
        \hfill 
        \noindent \textbf{Expected Graduation:} May 2024 \\
        Bachelor of Arts in Computer Science, Minor in Data Science \hfill \textbf{GPA:} 3.7

    \vspace{2.5mm}

    \noindent \textbf{Relevant Coursework:}
        Structure and Interpretation of Computer Programs, 
        Data Structures,
        Machine Structures,
        Discrete Math and Probability Theory, 
        Designing Information Devices and Systems I\&II,
        Database Systems,
        Computer Security,
        Foundations of Data Science,
        Principles and Techniques of Data Science, \\
        Human Contexts and Ethics of Data,
        Advanced Linux System Administration
        
    \header{PROJECTS \& RELEVANT EXPERIENCE}

    \noindent \textbf{Undergraduate Research Apprentice Program} \hfill Spring 2023 -- Present
    \\ \textit{Data Science Student Researcher}
    \begin{itemize}
        \item Researching under Professor Johnathan Marshall in the UC Berkeley Legal Studies Department.
        \item Using text data mining to understand patterns and changes in 18th-19th Century criminal law.
        \item Constructing RegEx classifiers to impute class on 16,000+ Old Bailey Online corpus criminal cases.
    \end{itemize}

    \vspace{2mm}

    \noindent \textbf{"Gitlet"} -- Java \hfill Fall 2021 
    \begin{itemize}
        \item Custom version control system modeled with functionality modeled after Git.
        \item Supports file tracking, branching, merging, and remote repositories.
        \item Implemented custom data structures to enable constant-time file lookup, hashing to handle "diffs" and to prevent file collisions, and merge conflict handling.
    \end{itemize}

    \vspace{2mm}

    \noindent \textbf{Enigma Machine} -- Java \hfill Fall 2021
    \begin{itemize}
        \item Developed an emulator of a WW2 Enigma Machine that could encrypt and decrypt text using cryptographically accurate implementations.
        \item Object-Oriented design made use of custom data structures representing physical rotors, plugboard, and alphabets of actual machine to enable clean code, programmatic readability, and modularity.
    \end{itemize} 

    \vspace{2mm}

    \noindent \textbf{Weather Station} -- C, HTML, Javascript \hfill Spring 2021
    \begin{itemize}
        \item Designed a custom battery-powered Arduino weather monitoring circuit system which pushed data to a database on a locally hosted Linux web server, accessible to the internet. 
        \item Self-hosted website to display and visualize weather data and give users the ability to pull more recent weather measurements from the device.
    \end{itemize}

    \vspace{-2mm}

    \header{SKILLS}

    \noindent \textbf{Languages}: Python, Java, C, Golang, SQL, Assembly, HTML, CSS, Javascript, PHP, Swift
    
    \vspace{2mm}

    \noindent \textbf{Tools:} Git, NumPy, Pandas, Matplotlib, Seaborn, Scikit-learn, Docker, \LaTeX, GDB, Linux Systems \& Servers, MongoDB, RegEx, XArray


    % \vspace{-2mm}

    \header{LEADERSHIP \& EXTRACURRICULARS}
    
    \noindent \textbf{Eagle Scout} \hfill 2009 -- 2020
    \begin{itemize}
        \item Demonstrated leadership, logistical, and communication expertise by coordinating multiple backpacking trips of up to 14 days and 100 miles.
        \item Facilitated meetings of 30+ Scouts, organized activites and taught practical and wilderness skills.
    \end{itemize}

    \vspace{2mm}

    \noindent \textbf{Jamba Juice} \hfill Summer 2021
    \\ \textit{Team Lead}
    \begin{itemize}
        \item Experience in a fast-paced customer-oriented work environment where precision and orchestration of many concurrent tasks was crucial. Promoted to 'Team Lead' within three weeks after demonstrating superior leadership and organizational skills. 
    \end{itemize}

    
\end{document}
